---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit then 'knit' that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fda

<!-- badges: start -->
[![R-CMD-check](https://github.com/JamesRamsay5/fda/workflows/R-CMD-check/badge.svg)](https://github.com/JamesRamsay5/fda/actions)
<!-- badges: end -->

The 'fda' package supports functional data analysis in R, as described in [Ramsay, Hooker, and Graves (2009) Functional Data Analysis with R and MATLAB (Springer)](https://www.amazon.com/Functional-Data-Analysis-MATLAB-Use/dp/0387981845)

## Installation

You can install the released version of fda from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("fda")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JamesRamsay5/fda")
```
## Example

The `fda` package comes with script files that run nearly all the examples in Ramsay, Hooker and Graves (2009).  You can find the script files as follows:  

```{r example}
library(fda)
(scripts <- system.file('scripts', package='fda')) 
```

EXCEPT:  These 'scripts' files are no longer in the package.  